---
title: "EDLD Lab2"
author: "Ksenia Gordeeva"
date: "4/17/2022"
output:
  html_document:
    toc: true
    toc_float: true

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(tidyverse)
library(rio)
library(here)
library(ggplot2)
#install.packages("repurrrsive")
library(repurrrsive)
library(httr)
```

### Part A Multiple Models

```{r load_data, include=FALSE}
file <- "https://github.com/datalorax/esvis/raw/master/data/benchmarks.rda"
load(url(file))
head(benchmarks)
```

```{r recode}
#Recode season to wave
benchmarks <- benchmarks %>%
	as_tibble() %>%
	mutate(wave = case_when(season == "Fall" ~ 0,
	                        season == "Winter" ~ 1,
	                        TRUE ~ 2))
```

1. Fit a model of the form `lm(math ~ wave)` for each student.


```{r}
split_df <- split(benchmarks, benchmarks$sid) 
models <- map(split_df, ~ lm(math ~ wave, data = .x))
coefs <- map(models, coef) 
ints <- map_dbl(coefs, 1)
slopes <- map_dbl(coefs, 2)


to_plot <- tibble(sid = names(split_df),
                  slope = slopes,
                  intercept = ints)
```

2. Reproduce the plot

```{r}
ggplot(benchmarks, aes(wave, math)) +
  geom_abline(
    aes(intercept = ints, 
        slope = slopes, 
        group = sid), 
    size = 0.01, 
    data = to_plot
  ) +
  geom_smooth(
    method = "lm",
    se = FALSE,
    color = "magenta",
    size = 2
  ) +
  scale_x_continuous(
    limits = c(0, 2),
    breaks = 0:2,
    labels = c("Fall", "Winter", "Spring")
  ) +
  scale_y_continuous(
    limits = c(115, 300)
  )
```

### Part B Star Wars 

1. Use the `sw_films` list to identify how many characters were represented in each film.
```{r}
films <- map_chr(sw_films, "title")
n_char <- map(sw_films, "characters") %>%
	map_dbl(length) %>%
	setNames(films)
n_char
```
2. Use the `sw_species` list to (a) identify species that have known hair colors and (b) identify what those hair colors are.
```{r}
tibble(species = map_chr(sw_species, "name"),
       hair = map_chr(sw_species, "hair_colors")) %>%
	filter(hair != "none" & hair != "n/a" & hair != "unknown")
```

### Part C: Some basic API calls

```{r}
ability1 <- GET("https://pokeapi.co/api/v2/ability/1") %>%
	content("parsed") 
```

1. Use {purrr} to write an API call to obtain data on the first five abilities (note, we're only using the first five to make the calls go fast, but the code would be essentially equivalent for any number of abilities you wanted to query). Make sure you parse the JSON data to a list.
```{r}
abilities <- paste0("https://pokeapi.co/api/v2/ability/", 1:5)
pokemon_ab <- map(abilities, GET) 
pokemon <- map(pokemon_ab, content, "parsed")
```

2. Use the parsed data to create a data frame that has the given ability, and the number of pokemon with that ability.
```{r}
pokemon_abilities <- tibble(ability = map_chr(pokemon, "name"),
                            n_pokemon = map_dbl(pokemon, ~length(.x$pokemon)))
pokemon_abilities
```

### Bonus
Create a new data frame that lists the names of the pokemon with these specific abilities.
```{r}
ability <- map_chr(pokemon, "name")
pokemon_name <- map(pokemon, ~map_chr(.x$pokemon, ~.x$pokemon$name))
tibble(pokemon_name, ability) %>% 
  unnest(pokemon_name)
```
